### 2024-07-12 README.Rmd
clean up targets and update readme with renv diagnostics.
add doi badge
Final published manuscript

@@

This repository contains the data and analysis used in the draft manuscript *"A  meta-analysis  of  the  impacts  of  best management  practices  on  nonpoint  source pollutant  concentration,"* by Schramm et al.

@@

```{r}
sessioninfo::session_info()
```

>>>>

# A  meta-analysis  of  the  impacts  of  best management  practices  on  nonpoint  source pollutant  concentration

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.10795231.svg)](https://doi.org/10.5281/zenodo.10795231)

@@

This repository contains the data and analysis used in:

Schramm, M., Kikoyo, D., Wright, J., Jain, S. (2024) [*"A  meta-analysis  of  the  impacts  of  best management  practices  on  nonpoint  source pollutant  concentration,"*](https://doi.org/10.3389/frwa.2024.1397615). Frontiers in Water. doi:10.3389/frwa.2024.1397615.

@@

```{r}
renv::diagnostics()
```
